Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-05-13 SIR_manuscript.tex
minor result was added

\item \label{p1:w} Increasing testing “focus” $\frac{w_I}{w_S}$ from random $w_S=w_I$ to targeted $w_S<w_I$ always decreases \Rnum.

@@

>>>>

\item \label{p1:w} Increasing testing “focus” $\frac{w_I}{w_S}$ from random, $w_S=w_I$, to targeted, $w_S<w_I$, always decreases \Rnum.

@@

Lastly, we show that increasing the focus of testing from random to targeted, always increases $\Delta$, thus decreases \Rnum. This can be seen in \fref{pan} and \fref{pan2}. In particular, we realize higher $\Delta$ levels, i.e., darker colors in corresponding plots\/facets as we go from panel~(a) to panel~(b) in the figures.
